Irt plot extra

### 2023-10-29 manuscript_SciRep.Rmd
added Text adjustments according to reviewers' comments in a copied RMD file (manuscript_SciRep) and added Siraji's predicitive validity study to the references.bib document (RL)

Furthermore, building on earlier attempts [e.g. @hubalek_ambulant_2006], there was a recent push toward the development and use of portable light loggers to improve ambulant light assessment and gain more insight into the NIF effects of light on human health in field conditions [@hartmeyer2022towards; @spitschan2022verification]. Attached to different body parts (e.g., wrist; head, at eye level; chest), these light loggers allow for the objective measurement of individual photic exposure patterns under real-world conditions and thus are valuable tools for field studies. Nevertheless, these devices also encompass limiting factors such as potentially being intrusive (e.g., when eye-level worn), yielding the risk of getting covered (e.g., when wrist- or chest-worn) and requiring (monetary) resources and expertise for acquisition and maintenance of the devices.

On the other hand, several attempts have been made to quantify received light exposure subjectively with self-report questionnaires (**Supplementary Table 1**), bypassing the cost and intrusiveness issues. However, subjective light intensity assessments pose a new set of challenges: The human visual system constantly adapts to brightness [@hurvich_perception_1966], while the signals underlying the non-visual effects of light are independent from perception [@allen_exploiting_2018], making the self-report assessment of light properties challenging. Retrospectively recalling the properties of a light source can further complicate such subjective evaluations. Moreover, measuring light properties alone does not yield any information about how individuals might behave differently regarding diverse light environments such as work, home or outdoors.

To date, little effort has been made to understand and capture these activities. Here, we present the development process of a novel self-reported inventory, the Light Exposure Behaviour Assessment (LEBA), for characterizing diverse light exposure-related behaviours.

@@

We observed that the response patterns of LEBA inventory for the entire sample (n=`r nrow(sem.data)`) were not normally distributed (Figures \@ref(fig:efagtPic1) and \@ref(fig:efagtPic2)). All items violated both univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality [@mardiaMeasuresMultivariateSkewness1970]. The multivariate skewness was`r printnum(mardia.all.data$b1p)` (p<0.001) and the multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p<0.001).

@@

In order to derive a short form of the LEBA inventory, we fitted each factor of the LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=690). The resulting item discrimination parameters of the inventory fell into categories of "very high" (10 items), "high" (4 items), "moderate" (4 items), and "low" ( 5 items), indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**). An examination of the item information curve (**Supplementary Figure 3**) revealed five items (1, 25, 30, 38, & 41) provided very low information regarding light exposure related behaviors with relatively flat curves (I($\theta$) \<0.20). We discarded those items, culminating in a short form of LEBA with five factors and 18 items (**Supplementary File 2**).

@@

Often psychological measurements require application of several questionnaires simultaneously. Responding to several lengthy questionnaires increases the participants losing focus and becoming tried. To avoid these situations we  derived a short version of the LEBA (18 items) using IRT analysis. We fitted a graded response model to the combined EFA and CFA sample (n=`r nrow(data)`) and discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20]. The resulting test information curves suggest that the short-LEBA is a psychometrically sound measure with adequate coverage of underlying traits and can be applied to capture the frequency of different light exposure related behaviours reliably.

@@

To our knowledge, the LEBA is the first inventory characterising light exposure-related behaviour in a scalable manner. Thus, estimating convergent validity with similar subjective scales was impossible. Alternatively, the validity of the LEBA could be evaluated by administering it conjointly with objective field measurements of light exposure (e.g. with portable light loggers, see literature review). By this route, one could study how the (subjectively measured) light exposure-related behavioural patterns translate into (objectively measured) received light exposure.

@@

The present article is a fully reproducible open access "R Markdown" document. All code and data underlying this article is available on a public [GitHub repository](https://github.com/leba-instrument). The English version of long and short form of LEBA  inventory and online survey implementation templates on common survey platforms(Qualtrics and REDCap) -- is available  on another public [GitHub repository](https://github.com/leba-instrument/leba-instrument-en) as well as on the dedicated [website](https://leba-instrument.org/) of the LEBA inventory under an open-access licence (Creative Commons CC-BY-NC-ND).

>>>>

Furthermore, building on earlier attempts [e.g. @hubalek_ambulant_2006], there was a recent push toward the development and use of portable light loggers to improve ambulant light assessment and gain more insight into the NIF effects of light on human health in field conditions [@hartmeyer2022towards; @spitschan2022verification]. Attached to different body parts (e.g., wrist; head, at eye level; chest), these light loggers allow for the objective measurement of individual photic exposure patterns under real-world conditions and thus are valuable tools for field studies. Nevertheless, these devices also encompass limiting factors such as potentially being intrusive (e.g., when eye-level worn), yielding the risk of getting covered (e.g., when wrist- or chest-worn) and requiring (monetary) resources and expertise for acquisition and maintenance of the devices. Moreover, it is important to note that portable light loggers alone do not collect data on the specific behavioural patterns in relation to light exposure.

On the other hand, several attempts have been made to quantify received light exposure subjectively with self-report questionnaires (**Supplementary Table 1**), bypassing the cost and intrusiveness issues. However, self-reporting light properties could be challenging for people who lack technical knowledge of light sources. Moreover, individuals may need to consider that, unlike a photometer, the human visual system continuously adapts to brightness [@hurvich_perception_1966], while the signals underlying the non-visual effects of light are independent from perception [@allen_exploiting_2018]. Retrospectively recalling the properties of a light source can further complicate such subjective evaluations. Moreover, measuring light properties alone does not yield any information about how individuals might behave differently regarding diverse light environments such as work, home or outdoors.

To date, little effort has been made to understand and capture these activities. Here, we present the development process of a novel self-reported inventory, the Light Exposure Behaviour Assessment (LEBA), for characterizing diverse light exposure-related behaviours. Notably, we do not claim to be estimating the personal light exposure with these questions. Instead, we aim to assess, in a scalable way, how people behave in relation to light, focusing on habitual patterns that could guide behavioural intervention points.

@@

We observed that the response patterns of LEBA inventory for the entire sample (n=`r nrow(sem.data)`) were not normally distributed (Figures \@ref(fig:efagtPic1) and \@ref(fig:efagtPic2)). All items violated both univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality [@mardiaMeasuresMultivariateSkewness1970]. The multivariate skewness was `r printnum(mardia.all.data$b1p)` (p<0.001) and the multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p<0.001).

@@

Our aim was to provide a data-driven approach to reducing the number of items for cases where a small reduction of items is necessary. In order to derive a short form of the LEBA inventory, we fitted each factor of the LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=690). The resulting item discrimination parameters of the inventory fell into categories of "very high" (10 items), "high" (4 items), "moderate" (4 items), and "low" ( 5 items), indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**). An examination of the item information curve (**Supplementary Figure 3**) revealed five items (1, 25, 30, 38, & 41) provided very low information regarding light exposure related behaviors with relatively flat curves (I($\theta$) \<0.20). We discarded those items, culminating in a short form of LEBA with five factors and 18 items (**Supplementary File 2**).

@@

Often psychological measurements require application of several questionnaires simultaneously. Responding to several lengthy questionnaires increases the participants losing focus and becoming tried. Thus, in some circumstances, reducing the number of items even slightly may be necessary to employ the LEBA questionnaire. Our aim was to provide a data-driven approach to reducing the number of items, apart from the possibility of excluding a specific factor from the 23-item questionnaire. Nonetheless, where possible, we strongly recommend using the extended form of the questionnaire to avoid limiting the range of gained information. We derived a short version of the LEBA (18 items) using IRT analysis. We fitted a graded response model to the combined EFA and CFA sample (n=`r nrow(data)`) and discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20]. The resulting test information curves suggest that the short-LEBA is a psychometrically sound measure with adequate coverage of underlying traits and can be applied to capture the frequency of different light exposure related behaviours reliably.

@@

To our knowledge, the LEBA is the first inventory characterising light exposure-related behaviour in a scalable manner. Thus, estimating convergent validity with similar subjective scales was impossible. However, a recent study [@Siraji.2023] demonstrated the predictive validity of the questionnaire by correlating the LEBA factors with chronotype, mood, sleep quality, and memory and concentration difficulties. 
In addition, further evidence for the validity of the LEBA could be obtained by administering it conjointly with objective field measurements of light exposure (e.g. with portable light loggers/wearables, see literature review), smartphone readouts as well as subjective data in the form of 24-hour recalls. By this route, one  could study how the (subjectively measured) light exposure-related behavioural patterns translate into (objectively measured) received light exposure, (objectively measured) smartphone use, and how closely the retrospective questionnaire relates to daily reports of these behaviours.

@@

The present article is a fully reproducible open access "R Markdown" document. All code and data underlying this article is available on a public [GitHub repository](https://github.com/leba-instrument). The English version of long and short form of LEBA  inventory and online survey implementation templates on common survey platforms (Qualtrics and REDCap) -- is available  on another public [GitHub repository](https://github.com/leba-instrument/leba-instrument-en) as well as on the dedicated [website](https://leba-instrument.org/) of the LEBA inventory under an open-access licence (Creative Commons CC-BY-NC-ND).
